Using Scagnostics to find Interesting Projections of Multivariate Data

### 2018-09-10 scagnostics.Rmd
Temporal traces working.

## Smoothness
We first study the smoothness of the scagnostics measures calculated on a sequence of 2-d projections obtained via an interpolated grand tour path. The temporal trace of a selected set of measures is shown below, where each time step refers to an interpolation step.

@@

```{r getProj}
getProj <- function(df, tPath, nameStr){
  sc <- NULL
  n <- length(tPath)
  df <- rescale(df)
  for (i in 1:n) {
  dprj <- df %*% tPath[[i]]
  #FIXME not only scagnostics but all relevant!
  #also keep track of t=i, and nameStr
  #after want to be able to directly plot full comparison.
  sc <- rbind(sc, scagnostics(dprj))
}
}
```

```{r grandtourpath}
set.seed(1988)
t1 <- save_history(sphere100, grand_tour(2), max=4)
t1full <- as.list(interpolate(t1))
n <- length(t1full)
sc <- NULL
for (i in 1:n) {
  dprj <- as.matrix(geoCombined) %*% t1full[[i]]
  sc <- rbind(sc, scagnostics(dprj))
}
#sc <- as.data.frame(sc)
#sc$t <- 1:n
#scPairs <- sc
#sc <- sc %>% gather(index, value, -t)
#```

#```{r plotscagGeozoo, fig.width=6, fig.height=7, fig.cap="Short tour paths with scagnostics computed on #projections. Most of the indices exhibit sharp jumps in scagnostic value."}
#ggplot(sc, aes(x=t, y=value)) + geom_line() + 
#  facet_wrap(~index, ncol=1, scales = "free_y") +
#  geom_vline(mapping = aes(xintercept=24, color="red")) +
#  geom_vline(mapping = aes(xintercept=39, color="red")) +
#  guides(color=FALSE)
#```

>>>>

## Smoothness
We first study the smoothness of the scagnostics measures calculated on a sequence of 2-d projections obtained via an interpolated grand tour path. The temporal trace of a selected set of measures is shown below, where each time step refers to an interpolation step. Note that each parameter range has been rescaled to be between [0,1] for direct comparison.

@@

```{r getProj}
getProj <- function(df, tPath, nameStr, size){
  sc <- tibble(convex=numeric(),
               clumpy=numeric(),
               skinny=numeric(),
               stringy=numeric(),
               dcor2d=numeric(),
               splines2d=numeric(),
               MIC=numeric(),
               TIC1=numeric(),
               t=numeric(),
               name=character(),
               size=numeric())
  n <- length(tPath)
  df <- rescale(df)
  for (i in 1:n) {
    dprj <- df %*% tPath[[i]]
    scagRes <- scagnostics(dprj)
    dcorRes <- dcor2d(dprj[,1], dprj[,2])
    splineRes <- splines2d(dprj[,1], dprj[,2])
    mineRes <- mine(dprj[,1], dprj[,2])
    sc <- add_row(sc, convex=scagRes["Convex"],
                  clumpy=scagRes["Clumpy"], skinny=scagRes["Skinny"],
                  stringy=scagRes["Stringy"], dcor2d=dcorRes,
                  splines2d=splineRes, MIC=mineRes$MIC,
                  TIC1=mineRes$TIC, t=i, name=nameStr, size=size)
  }
  maxTIC <- max(sc$TIC1)
  sc <- sc %>%
    mutate(TIC = TIC1/maxTIC) %>%
    select(-TIC1)

  return(sc)
}
```

```{r grandtourpath}
set.seed(1988)
t1 <- save_history(sphere100, grand_tour(2), max=4)
t1full <- as.list(interpolate(t1))
fullRes <- getProj(sin100, t1full, "sin", 100) %>%
  rbind(getProj(sin1000, t1full, "sin", 1000)) %>%
  rbind(getProj(sphere100, t1full, "sphere", 100)) %>%
  rbind(getProj(sphere1000, t1full, "sphere", 1000)) %>%
  rbind(getProj(pipe100, t1full, "pipe", 100)) %>%
  rbind(getProj(pipe1000, t1full, "pipe", 1000))
```

```{r plotgrandtour, fig.width=6, fig.height=7, fig.cap="Short tour paths with scagnostics computed on projections. Most of the indices exhibit sharp jumps in scagnostic value."}
fullResMelt <- melt(fullRes, id=c("t", "name", "size"))
ggplot(fullResMelt, aes(x=t, y=value)) +
  geom_line(aes(color=name, linetype=factor(size))) + 
  facet_wrap(~variable, ncol=1, scales = "free_y")
```
